%----package config


\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{multicol}

\usepackage[scale=0.80]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name


%----cv title


\firstname{\textcolor{gray}{Madushan}} % Your first name
\familyname{Nishantha} % Your last name

\title{DevOps Engineer}
%\address{"Samanpaya", Hangamuwa}{Ratnapura}
\mobile{(+94) 71 5593 430}
%%\phone{(000) 111 1112}
%%\fax{(000) 111 1113}
\email{j.l.madushan@gmail.com}
\extrainfo{\homepagesymbol github: \httplink{git.io/vXEkx} \\%
\homepagesymbol linkedin: \httplink{goo.gl/yR9Xgm}
}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%%\quote{"A witty and playful quotation" - John Smith}

%----the actual document

\begin{document}

\makecvtitle % Print the CV title
%\section{Contact Info}
%\cvitem{Full Name}{Johan Leman Madushan Nishantha Weerawardhana}
%\cvitem{Mobile}{(+94) 71 5593 430}
%\cvitem{Email}{\href{mailto:jlmadushan@gmail.com}{jlmadushan@gmail.com} / \href{mailto:madushan@kadira.io}{madushan@kadira.io}}
%\cvitem{Linkedin}{\href{https://lk.linkedin.com/in/madushan1000}{https://lk.linkedin.com/in/madushan1000}}
%\cvitem{Github}{\href{https://github.com/madushan1000}{https://github.com/madushan1000}}

\section{Summary}
\cvitem{}{
Excellent skills in building, maintaining, and troubleshooting Linux-based cloud application stacks on cloud services (such as Google compute/container engine, Amazon ec2/lambda, Azure, or Heroku), and using technologies (including node.js/es6/babel, meteor.js, golang, docker, kubernetes, and puppet). \newline
Hands-on software development experience includes building deployment automation tools such as meteor-up, or creating compiler plugin babel-plugin-react-docgen.
}


\section{Professional Experiences}

\cvitem{01/2017 \newline-- Present}{\large{\textbf{System Engineer at Pearson Lanka. -- System Administrator, Platform OS team}}}

\subsection{Linux server provisioning and orchestration}
\cvitem{}{RHEL, CentOS, and Ubuntu provisioning and orchestration using tools like puppet, RedHat satellite and the open source alternative The Foreman, virtualization platforms like VMware ESXI or VCenter.}

\subsection{Task automation using Bladelogic server automation toolkit}
\cvitem{}{Automation and execution of routine tasks across thousands of Pearson estate Linux servers.}

\subsection{Monthly patching operations}
\cvitem{}{Contributing to the Linux global monthly patching operations across Pearson estate including troubleshooting and remediation of any issues occurs while patching Linux distributions like RHEL, CentOS or Ubuntu.}

\subsection{Incident/Change management with ServiceNow}
\cvitem{}{Interacting daily with ITIL compatible ServiceNow platform to resolve and document any Linux related incident or change occur in Pearson server estate. \newline}


\cvitem{10/2015 \newline-- 01/2017}{\large{\textbf{System administrator at Kadira, Inc. -- DevOps and system reliability engineering}}}

\subsection{Storybook hub\href{https://hub.getstorybook.io}{(hub.getstorybook.io)}}
\cvitem{}{Development and deploy automation of \href{https://getstorybook.io}{React Storybook} build and hosting service Storybook Hub.}

\subsection{{Improving organizational security at Kadira}\href{https://goo.gl/YZEJHl}{(goo.gl/YZEJHl)}}
\cvitem{}{Designing and implementing a system to centralize back-end (aws/gcloud/etc...) authentication methods (ssh/passwords/etc...) used by Kadira's various projects.}

\clearpage

\subsection{{Meteor Up}\href{https://git.io/vXEKA}{(git.io/vXEKA)}}
\cvitem{}{The production quality Meteor deployment tool, Meteor Up, which enables developers to deploy their meteor applications to custom Linux servers. One of the maintainers of this open-source project.}

\subsection{{Storybook ping receiver}\href{https://git.io/vXE9L}{(git.io/vXE9L)}}
\cvitem{}{A proxy for react storybook npm package usage meta-data collection. Behind the scenes, it streams analytics data directly to Google BigQuery and provides a GraphQL API to query and interact with the data for its react storybook client}

\subsection{{Babel Plugin React Docgen}\href{https://git.io/vXE6k}{(git.io/vXE6k)}}
\cvitem{}{\href{https://babeljs.io/}{Babeljs} javascript transpiler plugin to inject proptype documents in to \href{https://facebook.github.io/react/}{React} component classes, making use of the babeljs plugin API and node.js/ES6 \newline}


\cvitem{10/2014 \newline -- 03/2015}{\large{\textbf{Short-term technical training at Atrenta Lanka (PVT) LTD -- Software engineering intern at GUI team}}}

\subsection{SpyGlass Qt GUI test automation using \href{https://www.froglogic.com/squish/gui-testing/}{Squish} framework}
\cvitem{}{Created a program to filter out additional code generated while the initial test generation to make test replay work; integrated Qt GUI testing into the automated regression workflow.}

%\subsection{SpyGlass Qt GUI bug fixes}
%\cvitem{}{Contributions to the new SpyGlass Qt GUI using Qt framework and C++, and a number of Coverity static code analyzer issue resolutions on the codebase.}

%\section{Technical  Skills}

%\cvitem{}{Cloud architecture, deploy automation, containerization, and virtualization}
%\cvitem{}{--- AWS ec2/lambda, gcloud(gce, gke), heroku, docker, kubernetes, VMware }
%\cvitem{}{Database administration} 
%\cvitem{}{--- MongoDB}
%\cvitem{}{Software Defined Networking} 
%\cvitem{}{--- Open vSwitch, OpenDaylight}

%\section{Programming Skills}

%\cvitem{Advanced}{ JavaScript/ES6, C/C++, Python}
%\cvitem{Intermediate}{Golang, Rust, Haskell, Common Lisp, Antlr, Perl, Assembly, Java}

\section{Education}

\cventry{2011--2015}{Bachelor of Engineering (B.Sc.)}{University of Peradeniya, Sri Lanka}{}{}{Computer Engineering, Graduate}  % Arguments not required can be left empty
%\cventry{2002--2010}{High School}{Sivali Central Collage}{Ratnapura, Sri Lanka}{}{Specialized in Science (Mathematics)}

\section{Other Projects}

\subsection{\href{https://sdntestbed.wordpress.com/}{SDN testbed for research and education -- University Final Year Project}}
\cvitem{}{Low-cost software defined networking testbed built using raspberry pi devices for researche and undergraduate work.}

\subsection{Virtual memory management system -- OS161}
\cvitem{}{Designing and implementing a virtual memory management system for educational operating system OS161.}

\subsection{\href{http://forum.xda-developers.com/showthread.php?t=2468230}{Porting Firefox OS (B2G) to HTC Desire HD}}
\cvitem{}{Solo project of porting Firefox OS, aka Boot to Gecko (B2G), to HTC Desire HD smartphone.}

\subsection{\href{http://goo.gl/wXlQa1}{Contributions to Firefox for android -- fenek}}
\cvitem{}{Code cleanups and improvements to Firefox for android}

\subsection{User level thread library -- C}
\cvitem{}{Designing and implementing of context switching library for user level C programs.}

%\subsection{OCR based chemical reaction solver -- Android}
%\cvitem{}{An android application which uses Google's tesseract OCR engine to identify chemical reactions printed on paper and return the reaction result.}

%\subsection{Seven Segment Display Decoder for hexadecimal numbers -- FPGA}
%\cvitem{}{ Designing and implementing a decoder for displaying hexadecimal numbers in seven segment displays on Altera DE2 FPGA development board using VHDL.}



%       INTERESTS SECTION

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Operating systems}{Embedded designing}
\cvlistdoubleitem{Virtualization}{Programming languages}
\cvlistdoubleitem{Network security}{Reverse engineering}
\cvlistdoubleitem{Hiking}{Creative writing}

\clearpage

%\section{Referees}
%\begin{multicols}{2}

%\cvitem{}{Dr. Manjula Sandirigama}
%\cvitem{}{Department of Computer Engineering,}
%\cvitem{}{Faculty of Engineering,}
%\cvitem{}{University of Peradeniya.}
%\cvitem{T.P.:}{(+94) 71 8385 968}
%\cvitem{Email:}{\href{mailto:m\_sandirigama@ce.pdn.ac.lk}{m\_sandirigama@ce.pdn.ac.lk}}

%\cvitem{}{Arunoda Susiripala}
%\cvitem{}{CEO, Kadira, Inc.}
%\cvitem{}{Colombo 4}
%\cvitem{}{Sri Lanka}
%\cvitem{T.P.:}{(+94) 77 644 8826}
%\cvitem{Email:}{\href{mailto:arunoda@kadira.io}{arunoda@kadira.io}}

%\columnbreak 

%\cvitem{}{Dr. Dhammika Elkaduwe}
%\cvitem{}{Department of Computer Engineering}
%\cvitem{}{Faculty of Engineering}
%\cvitem{}{University of Peradeniya}
%\cvitem{T.P.:}{ (+94) 81 2393 914}
%\cvitem{Email:}{\href{mailto:dhammika@ce.pdn.ac.lk}{dhammika@ce.pdn.ac.lk}}

%\end{multicols}

%\section{Declaration}
%\cvitem{}{ I hereby certify that the above information is true and correct to the best of my knowledge and belief}
%\setfont[Language=Sinhala]{BhashitaComplex.ttf} 
%\cvitem{}{මදුශාන්}

%\cvitem{}{J.L.M.N. Weerawardhana}



%----------------------------------------------------------------------------------------
%       COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
